\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-27 ase20/eval.tex
[ASE] Revised Evaluation section

\( \tool \) targets ECMAScript specifications released after ES7 in 2016 because
our tool utilizes common patterns in the converged writing style since ES7 as
already explained in Section~\ref{sec:overview}.  Thus, we evaluate the coverage
of \( \tool \) by applying it to the most recent four versions of ECMAScript,
ES7 to ES10.  We measured for how many grammar productions and steps in abstract
algorithms \( \tool \) automatically generates parsers and AST-IR translators,
respectively, in two respects: 1) in each version and 2) in each difference
between adjacent versions.

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.pdf}
    \caption{Results for existing versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-diff.pdf}
    \caption{Results for differences between adjacent versions}
    \label{fig:semantics-all-version-diff}
  \end{subfigure}
  \caption{Number of abstract algorithm steps in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\vspace*{-1em}
\end{figure}

For semantics, Figure~\ref{fig:all-version} shows that \( \tool \) automatically
compile algorithm steps to the corresponding \( \ires \) instructions with
\inred{91.60\%} success rate on average for existing specifications, and
\inred{90.43\%} for updates.  ECMAScript abstract algorithms describe not only
core language semantics but also other helper functions of built-in libraries.
Built-in libraries written in more diverse styles in describing their own
specific functionalities.  Thus, built-in libraries have lower success rates
(\inred{86.98\%} for specifications and \inred{86.09\%} for updates) than core
language semantics (\inred{95.35\%} for specifications and \inred{95.25\%} for
updates).

@@

To define the \textit{first IR-based formal semantics of modern JavaScript}, we
completed missing parts of the AST-IR translator for ES10.  Among \inred{9,674}
steps in ES10, \inred{8,901} steps are automatically compiled via
\textsf{Algorithm Compiler}.  Among the remaining \inred{773} steps, we manually
implemented all remaining language semantics (\inred{221} steps) and essential
parts of built-in libraries (\inred{XX} steps out of \inred{552}) in \inred{XX}
days.  Moreover, we manually implemented the \textsf{Global Setting} as described
in Section~\ref{sec:compiler-impl} for the core language features.  However, we
do not support several minor language features that do not affect the overall
JavaScript semantics critically: non-strict mode codes, modules, early errors
before actual executions, and inessential built-in objects.

Thanks to the executability of our extracted formal semantics, we checked the
semantics with Test262, the official conformance test suite provided by TC39.
We fixed version of Test262 as of February 28, 2019 because the ES10 was
branched out with the branch name es2019 in that day.  While it consists of
\inred{XX,XXX} tests, we filtered out \inred{XX,XXX} tests not applicable for
our formal semantics as shown in Table~\ref{table:test262}.  Test262 targets not
only the current official version of ECMAScript but several extensions and
in-progress features. We excluded \inred{X,XXX} tests for such cases to focus on
the semantics of ES10.  Among \inred{XX,XXX} ES10 tests, we also filtered out
\inred{X,XXX} tests using language features not supported by our semantics.

\begin{table*}[t]
  \centering
  \caption{Specification errors and wrong tests in Test262.}
  \label{table:spec-tests-errors}
  \vspace*{-0.5em}
  \small
  \begin{tabular}{|c|c|l|c|c|c|c|c|}
    \hline
    \multicolumn{1}{|c|}{\bf Name} &
    \multicolumn{1}{c|}{\bf Feature} &
    \multicolumn{1}{c|}{\bf Description} &
    \multicolumn{1}{c|}{\bf Known} &
    \multicolumn{1}{c|}{\bf Created} &
    \multicolumn{1}{c|}{\bf Resolved} &
    \multicolumn{1}{c|}{\bf Existed} &
    \multicolumn{1}{c|}{\bf \# Failed Tests} \\\hline

    es10-1 &
    Await &
    \makecell[l]{Passing wrong type of \\ the second argument for {\bf PromiseResolve}.} &
    \textsf{O} &
    2019-02-27 &
    2019-04-13 &
    45 days &
    1100 \\\hline

    es10-2 &
    IterationKind &
    \makecell[l]{Missing \code{async-iterate} case \\ in the assertion of {\bf
    ForIn/OfHeadEvaluation}.} &
    \textsf{X} &
    2018-02-16 &
    2020-03-25 &
    768 days &
    1120 \\\hline

    es10-3 &
    Completion &
    \makecell[l]{Not handling abrupt completion \\ in {\bf Evaluation} of {\it
    EqualityExpression}.} &
    \textsf{O} &
    2016-06-01 &
    2019-05-02 &
    1065 days &
    1 \\\hline

    es10-4 &
    Function &
    \makecell[l]{No semantics of {\bf IsFunctionDefinition} \\ for
    \code{function(...)\{...\}}.} &
    \textsf{O} &
    2015-10-30 &
    2020-01-18 &
    1541 days &
    \inred{XX} \\\hline

    es10-5 &
    ForOf &
    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
    await(var x of e)\{...\}}.} &
    \textsf{O} &
    2018-02-16 &
    2019-10-11 &
    602 days &
    0 \\\hline

    es10-6 &
    Argument &
    \makecell[l]{No semantics of {\bf ExpectedArgumentCount} \\ for the base case
    of {\it FormalParameters}.} &
    \textsf{O} &
    2016-11-02 &
    2020-02-20 &
    1205 days &
    \inred{XX} \\\hline

    es10-7 &
    String &
    \makecell[l]{Wrong use of \code{=} operator in {\bf
    StringGetOwnProperty}.} &
    \textsf{X} &
    2015-06-01 &
    \inred{2019-00-00} &
    \inred{XX} days &
    \inred{XX} \\\hline

    test-1 &
    Global &
    \makecell[l]{Testing implementation-dependent [[Prototype]] \\ of the global
    object.} &
    \textsf{X} &
    \inred{2019-00-00} &
    \inred{2019-00-00} &
    \inred{XX} days &
    10 \\\hline

    bigint-1 &
    UpdateExpression &
    \makecell[l]{Using wrong variable \code{oldvalue} instead of \\
    \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    bigint-2 &
    NumberOp &
    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} \\ in {\bf
    Number::unsignedRightShift}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    bigint-3 &
    NumberOp &
    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} \\ in {\bf
    NumberBitwiseOp}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

@@

\begin{table}[t]
  \centering
  \caption{Excluded tests in Test262}
  \label{table:test262}
  \vspace*{-0.5em}
  \small
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \inred{\textbf{XX,XXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes & \inred{XXX}\\\hdashline
    Internationalization & \inred{XXX}\\\hdashline
    In-progress features & \inred{X,XXX}\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ES10 Tests} & \inred{\textbf{XX,XXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict modes & \inred{X,XXX}\\\hdashline
    Modules & \inred{X,XXX} \\\hdashline
    Early errors & \inred{X,XXX} \\\hdashline
    Inessential built-in objects & \inred{X,XXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \inred{\textbf{XX,XXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XX,XXX} \\\hdashline
    Failed tests & \inred{XXX} \\\bottomrule
  \end{tabular}
  \vspace*{-2em}
\end{table}

For \inred{XX,XXX} applicable tests, the synthesized JavaScript parser
successfully parses all tests but \inred{XXX} tests are failed to be executed
because of the different semantics between ECMAScript and official tests.  Based
on the failed tests, we found 7 specification errors in ES10 and 10 wrong tests
in Test262 as described in Table~\ref{table:spec-tests-errors}.  For example,
the specification error es10-1 is related to the JavaScript Await.  The {\bf
PromiseResolve (C, x)} algorithm creates a new Promise object using a given
constructor {\bf C} and resolved with a given value {\bf x}.  However, a
specification update added three invocations of {\bf PromiseResolve} with a list
of values for {\bf x} in February 27, 2019.  This error exists in 45 days until
April 13, 2019 and fails \inred{XX} tests for ES10 in Test262.  For other cases,
es10-2 arises because of the wrong assertion. es10-3 and es10-7 arise because
contributors misunderstood the meaning of abrupt completion and \code{=}
operator for numbers, respectively.  es10-4, es10-5, and es10-6 are
specification errors that miss or define twice specific corner cases of
semantic.  For example, es10-4 is an error that does not define the {\bf
IsFunctionDefinition} algorithm for unnamed functions such as
\code{function(){}}.  For these seven specification errors, they existed in ES10
in \inred{XXX} days on average.  Besides, two errors es10-2 and es10-7 are even
not known before we reported to TC39.

For tests in Test262, we found 10 wrong tests categorized in test-1 and they are
related to the JavaScript global object. The [[Prototype]] internal property of
the global object is fully implementation dependent thus the official tests
should not check its attributes.  However, 10 tests assumes that [[Prototype]]
of the global object is a prototype chain starts with \code{Object.prototype}.
They violate the implementation dependent semantics of ES10.  Moreover, they
existed in Test262 in \inred{XXX} days.

After resolving above specification errors in ES10, we extracted formal
semantics from the revised specification again. The revised formal semantics of
ES10 passed all \inred{XX,XXX} applicable tests in Test262.  We believe that our
tool can assist to check and find bugs in ECMAScript by generating executable
formal semantics and executing it with tests in Test262.

@@

\begin{table}[t]
  \centering
  \caption{Evaluation result of \( \tool \) for Finished stage proposals that
  will be included in ES11.}
  \label{table:spec-prop-result}
  \vspace*{-0.5em}
  \small
  \begin{tabular}{c?r|r?r?r}
    \hline
    \multicolumn{1}{c?}{\multirow{2}{*}{\bf Name}} &
    \multicolumn{2}{c?}{\bf \( \Delta \) \# Prod.} &
    \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Steps}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}

@@

    \code{matchAll} of \code{String} &
    0 &
    0 &
    9/9 &
    5/5\\\hline

    \code{import()} &
    0 &
    2 &
    22/23 &
    0/0\\\hline

    \code{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207\\\hline

    \code{Promise.allSettled} &
    0 &
    0 &
    79/85 &
    50/50\\\hline

    \code{globalThis} &
    0 &
    0 &
    1/1 &
    1/1\\\hline

    \code{for-in} mechanics &
    0 &
    0 &
    36/37 &
    0/0\\\hline

    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19\\\hline

    Nullish Coalescing Op. &
    1 &
    4 &
    10/10 &
    21/21\\\hline

    \code{import.meta} &
    0 &
    2 &
    15/15 &
    0/0\\\hline

    {\bf Total} &
    8 &
    11 &
    502/577 &
    \inred{303}/303\\\hline
  \end{tabular}
\end{table}

Table~\ref{table:spec-prop-result} shows the result of applying \( \tool \) to 9
Finished proposals for ES11.  For all proposals, \inred{XX} lexical and
\inred{XX} syntactic productions are modified and \( \tool \) successfully
updated the changes to the synthesized JavaScript parser.  The updated parser
parses all applicable tests for all proposals.  For abstract algorithms,
\inred{XXX} steps out of \inred{XXX} steps are automatically converted to the
corresponding \( \ires \) instructions by the algorithm compiler without
changing of the compile rules.  Thus, our tool has \inred{XX.XX\%} success rate
on average for future proposals.  Similar with
Section~\ref{sec:check-with-tests}, we manually implemented missing part of the
AST-IR translator for each Finished proposal and checked each extracted
semantics with official tests.  Each of them passed all applicable tests except
the semantics for \code{BigInt} proposal.  It fails \inred{XX} tests out of 207
applicable tests.

Based on the failed tests, we found three undiscovered specification errors
(bigint-1, bigint-2, and bigint-3), and one reported error (bigint-4) in the
BigInt proposal as described in Table~\ref{table:spec-tests-errors}.  All of
them were confirmed by TC39 and will be fixed in the next release.  The BigInt
proposal added a new type of primitives BigInt and unified the type with
original Number type to Numeric types.  Thus, it not only added new
algorithms for BigInt but also modified all existing algorithms related to
number values.  The error bigint-1 is just a simple misuse of the variable
\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}. bigint-2 and
bigint-3 break the backward compatibility because of the incorrectly mixed uses
of {\bf ToInt32} and {\bf ToUint32} algorithms in unsigned right shift operators
and bitwise operators, respectively. The last one bigint-4 arises because the
Number constructor does not consider BigInt primitives.  On average, ECMAScript
included these four specification errors in \inred{XXX} days.

After fixing all specification errors, we extracted the semantics for the BigInt
proposal again.  The updated semantics passed all 207 applicable tests.  Thus,
\( \tool \) also correctly extract IR-based semantics from future proposals.

>>>>

\( \tool \) targets ECMAScript specifications released after ES7 in 2016 because
our tool utilizes common patterns in the converged writing style since ES7 as
already explained in Section~\ref{sec:overview}.  Thus, we evaluate the coverage
of \( \tool \) by applying it to the most recent four versions of ECMAScript,
ES7 to ES10.  We measured for how many grammar productions and steps in abstract
algorithms \( \tool \) automatically generates parsers and AST-IR translators,
respectively, in two respects: 1) in each version and 2) in each update between
adjacent versions.

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.pdf}
    \caption{Results for existing versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-update.pdf}
    \caption{Results for annual updates}
    \label{fig:semantics-all-version-update}
  \end{subfigure}
  \caption{Number of abstract algorithm steps in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\vspace*{-1em}
\end{figure}

For semantics, Figure~\ref{fig:all-version} shows that \( \tool \) automatically
compile algorithm steps to the corresponding \( \ires \) instructions with
\inred{91.38\%} success rate on average for existing specifications, and
\inred{92.08\%} for updates.  ECMAScript abstract algorithms describe not only
core language semantics but also other helper functions of built-in libraries.
Built-in libraries written in more diverse styles in describing their own
specific functionalities.  Thus, built-in libraries have lower success rates
(\inred{86.74\%} for specifications and \inred{88.24\%} for updates) than core
language semantics (\inred{95.14\%} for specifications and \inred{96.41\%} for
updates).

@@

To evaluate the correctness of \( \tool \), we utilizes Test262, the official
conformance test suite provided by TC39.  First, we complete missing parts of
the AST-IR translator for the latest version of ECMAScript (ES10). Then, we
test the extracted semantics of ES10 with Test262 and reason about the failed
tests.

To focus on core language semantics of JavaScript, we completed only necessary
parts in missing parts of AST-IR translator for ES10.  For abstract algorithms
in ES10, \inred{8,901} steps out of \inred{9,674} steps are automatically
compiled via \textsf{Algorithm Compiler} as described in
Figure~\ref{fig:all-version}(a).  Among the remaining \inred{773} steps, we
manually implemented all missing steps for core language semantics (\inred{221}
steps) and essential parts of built-in libraries (\inred{XX} steps out of
\inred{552}).  Moreover, we manually implemented the \textsf{Global Setting} as
described in Section~\ref{sec:compiler-impl} for the core language features.
However, we do not support several minor language features that do not affect
the overall JavaScript semantics critically: non-strict mode codes, modules,
early errors before actual executions, and inessential built-in objects.

\begin{table*}[t]
  \centering
  \caption{Specification errors in ES10 and in proposals that are ready for
  inclusion in ES11.}
  \label{table:spec-errors}
  \vspace*{-0.5em}
  \small
  \begin{tabular}{|c|c|l|c|c|c|c|c|}
    \hline
    \multicolumn{1}{|c|}{\bf Name} &
    \multicolumn{1}{c|}{\bf Feature} &
    \multicolumn{1}{c|}{\bf Description} &
    \multicolumn{1}{c|}{\bf Known} &
    \multicolumn{1}{c|}{\bf Created} &
    \multicolumn{1}{c|}{\bf Resolved} &
    \multicolumn{1}{c|}{\bf Existed} &
    \multicolumn{1}{c|}{\bf \# Failed Tests} \\\hline

    es10-1 &
    Condition &
    \makecell[l]{Ambiguous production rule for \\
    dangling \code{else} problem in {\it IfStatement}.} &
    \textsf{X} &
    2015-06-01 &
    \inred{2020-00-10} &
    \inred{XXX} days &
    1 \\\hline

    es10-2 &
    Await &
    \makecell[l]{Passing wrong type of \\ the second argument for {\bf PromiseResolve}.} &
    \textsf{O} &
    2019-02-27 &
    2019-04-13 &
    45 days &
    1100 \\\hline

    es10-3 &
    Iteration &
    \makecell[l]{Missing \code{async-iterate} case \\ in the assertion of {\bf
    ForIn/OfHeadEvaluation}.} &
    \textsf{X} &
    2018-02-16 &
    2020-03-25 &
    768 days &
    1120 \\\hline

    es10-4 &
    Completion &
    \makecell[l]{Not handling abrupt completion \\ in {\bf Evaluation} of {\it
    EqualityExpression}.} &
    \textsf{O} &
    2015-06-01 &
    2019-05-02 &
    1065 days &
    1 \\\hline

    es10-5 &
    String &
    \makecell[l]{Wrong use of \code{=} operator in {\bf
    StringGetOwnProperty}.} &
    \textsf{X} &
    2015-06-01 &
    \inred{2019-00-00} &
    \inred{XX} days &
    \inred{XX} \\\hline

    es10-6 &
    Function &
    \makecell[l]{No semantics of {\bf IsFunctionDefinition} \\ for
    \code{function(...)\{...\}}.} &
    \textsf{O} &
    2015-10-30 &
    2020-01-18 &
    1541 days &
    \inred{XX} \\\hline

    es10-7 &
    Function &
    \makecell[l]{No semantics of {\bf ExpectedArgumentCount} \\ for the base case
    of {\it FormalParameters}.} &
    \textsf{O} &
    2016-11-02 &
    2020-02-20 &
    1205 days &
    \inred{XX} \\\hline

    es10-8 &
    Iteration &
    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
    await(var x of e)\{...\}}.} &
    \textsf{O} &
    2018-02-16 &
    2019-10-11 &
    602 days &
    \inred{XX} \\\hline

    bigint-1 &
    Expression &
    \makecell[l]{Using wrong variable \code{oldvalue} instead of \\
    \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    bigint-2 &
    Number &
    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} \\ in {\bf
    Number::unsignedRightShift}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    bigint-3 &
    Number &
    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} \\ in {\bf
    NumberBitwiseOp}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

@@

To check the correctness of the extracted IR-based semantics using Test262, we
fixed version of Test262 as of February 28, 2019 because the ES10 was branched
out with the branch name es2019 in that day.  While it consists of
\inred{XX,XXX} tests, we filtered out \inred{XX,XXX} tests not applicable for
our formal semantics as shown in Table~\ref{table:test262}.  Test262 targets not
only the current official version of ECMAScript but several extensions and
in-progress features. We excluded \inred{X,XXX} tests for such cases to focus on
the semantics of ES10.  Among \inred{XX,XXX} ES10 tests, we also filtered out
\inred{X,XXX} tests using language features not supported by our semantics.

\begin{table}[t]
  \centering
  \caption{Test results for Test262}
  \label{table:test262}
  \vspace*{-0.5em}
  \small
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \inred{\textbf{XX,XXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes & \inred{XXX}\\\hdashline
    Internationalization & \inred{XXX}\\\hdashline
    In-progress features & \inred{X,XXX}\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ES10 Tests} & \inred{\textbf{XX,XXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict modes & \inred{X,XXX}\\\hdashline
    Modules & \inred{X,XXX} \\\hdashline
    Early errors & \inred{X,XXX} \\\hdashline
    Inessential built-in objects & \inred{X,XXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \inred{\textbf{XX,XXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XX,XXX} \\\hdashline
    Failed tests & \inred{XXX} \\\bottomrule
  \end{tabular}
  \vspace*{-2em}
\end{table}

For \inred{XX,XXX} applicable tests, the extracted semantics fails \inred{XXX}
tests.  We reason about the failed tests, and we discover that they failed
because ES10 actually has specification errors. We found eight specification
errors in ES10 (es10-1 to es10-9 in Table~\ref{table:spec-errors}).  Among them,
five errors are already fixed in the draft version of ECMAScript but three errors
are newly revealed.  We reported four new errors, and TC39 confirmed and
merged them into the current draft.

es10-1 is related to the dangling \code{else} problem introduced in ALGOL
60~\cite{dangling-else}. While ES10 describes the rule that the \code{else}
should be associated with the nearest \code{if}, the rule is not explicitly
represented in the ES10 grammar rule.  It causes one test failed and it is a not
yet discovered error.  Thus, we revised the grammar rule to satisfy this rule
and TC39 accepted it in \inred{May X, 2020}.

es10-2 is related to the JavaScript Await.  The {\bf PromiseResolve (C, x)}
algorithm creates a new Promise object using a given constructor {\bf C} and
resolved with a given value {\bf x}.  However, a specification update added
three invocations of {\bf PromiseResolve} with a list of values for {\bf x} in
February 27, 2019.  This error exists in 45 days until April 13, 2019 and causes
\inred{XX} tests failed.

es10-3 arises because of the wrong assertion. ES9 introduced \code{for await}
iteration statements thus it also introduced a new {\it iterationKind} tag,
\code{async-iterate}. However, \code{ForIn/OfHeadEvaluation} algorithm misses
the case of \code{async-iterate} in the assertion. It causes 1120 tests failed
and it is an unknown error. Thus, we revised the assertion to cover the
\code{async-iterate} case and TC39 accepted it in March 25, 2020.

es10-4 and es10-5 arise because contributors misunderstood the meaning of
operations used in abstract algorithms. Especially, es10-5 is related to
\code{=} operator for numbers and not yet discovered. In abstract algorithms,
``{\it x} = {\it y}'' denotes equality expression for double-precision 64-bit
binary format IEEE 754-2008 values thus ``+0 = -0'' is true. However, the {\bf
StringGetOwnProperty} algorithms uses ``{\it index} = -0'' to check whether
index is exactly same with -0 but it is true even if {\it index} is +0.

es10-6, es10-7, and es10-8 are errors that miss or define twice some parts of
cases in semantics. For example, es10-8 is an error that define the {\bf
VarScopedDeclarations} for \code{for await} iterations. If the choice is wrong,
\inred{XX} tests will be failed.

After resolving above specification errors in ES10, we extracted formal
semantics from the revised specification again. The revised formal semantics of
ES10 passed all \inred{XX,XXX} applicable tests in Test262.  \( \tool \) is
helpful to correctly extract semantics from ECMAScript but also to detect bugs
by directly check ECMAScript with Test262. Without our tool, above eight errors
existed in ECMAScript in \inred{XXX} days on average. Besides, three errors
es10-1, es10-3, and es10-5 are even not known before we reported to TC39. We
believe that \( \tool \) bridges gaps between ECMAScript and Test262.

@@

\begin{table}[t]
  \centering
  \caption{Evaluation result of \( \tool \) for Finished stage proposals that
  will be included in ES11.}
  \label{table:spec-prop-result}
  \vspace*{-0.5em}
  \small
  \begin{tabular}{c?r|r?r?r?r}
    \hline
    \multicolumn{1}{c?}{\multirow{2}{*}{\bf Name}} &
    \multicolumn{2}{c?}{\bf \( \Delta \) \# Prod.} &
    \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Steps}} &
    \multicolumn{1}{c?}{\multirow{2}{*}{\bf \( \Delta \) \# Tests}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\bf \# Tests}} \\\cline{2-3}

@@

    \code{matchAll} of \code{String} &
    0 &
    0 &
    9/9 &
    5/5 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \code{import()} &
    0 &
    2 &
    22/23 &
    0/0 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \code{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \code{Promise.allSettled} &
    0 &
    0 &
    79/85 &
    50/50 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \code{globalThis} &
    0 &
    0 &
    1/1 &
    1/1 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \code{for-in} mechanics &
    0 &
    0 &
    36/37 &
    0/0 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    Nullish Coalescing Op. &
    1 &
    4 &
    10/10 &
    21/21 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \code{import.meta} &
    0 &
    2 &
    15/15 &
    0/0 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    {\bf Total} &
    8 &
    11 &
    502/577\\\cline{1-4}
  \end{tabular}
\end{table}

Table~\ref{table:spec-prop-result} shows the result of applying \( \tool \) to 9
Finished proposals for ES11.  For all proposals, \inred{XX} lexical and
\inred{XX} syntactic productions are modified and \( \tool \) successfully
updated the changes to the synthesized JavaScript parser.  The updated parser
parses all applicable tests for all proposals.  For abstract algorithms,
\inred{XXX} steps out of \inred{XXX} steps are automatically converted to the
corresponding \( \ires \) instructions by the algorithm compiler without
changing of the compile rules.  Thus, our tool has \inred{XX.XX\%} success rate
on average for future proposals.  Similar with
Section~\ref{sec:check-with-tests}, we manually implemented missing part of the
AST-IR translator for each Finished proposal and checked each extracted
semantics with official tests.  Each of them passed all applicable tests except
the semantics for \code{BigInt} proposal.  It fails \inred{XX} tests out of 207
applicable tests for the proposal and \inred{XXXX} tests out of \inred{XXXXX}
applicable tests for ES10.

Based on the failed tests, we found three undiscovered specification errors
(bigint-1, bigint-2, and bigint-3), and one reported error (bigint-4) in the
BigInt proposal as described in Table~\ref{table:spec-errors}.  All of
them were confirmed by TC39 and will be fixed in the next release.  The BigInt
proposal added a new type of primitives BigInt and unified the type with
original Number type to Numeric types.  Thus, it not only added new
algorithms for BigInt but also modified all existing algorithms related to
number values.  The error bigint-1 is just a simple misuse of the variable
\code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}. bigint-2 and
bigint-3 break the backward compatibility because of the incorrectly mixed uses
of {\bf ToInt32} and {\bf ToUint32} algorithms in unsigned right shift operators
and bitwise operators, respectively. The last one bigint-4 arises because the
Number constructor does not consider BigInt primitives.  On average, ECMAScript
included these four specification errors in \inred{XXX} days.

After fixing all specification errors, we extracted the semantics for the BigInt
proposal again.  The updated semantics passed all 207 applicable tests for the
proposal and \inred{XXXXX} applicable tests for ES10.  Thus, \( \tool \) also
correctly extract IR-based semantics from future proposals.

### 2020-04-27 ase20/intro.tex
[ASE] Revised Evaluation section

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between tests and the specification
    written in a natural language.}
    Because the formal semantics automatically extracted by \( \tool \) is executable
    and its components have one-to-one correspondences with the components of
    ECMAScript, we can check the specification
    using the official test conformance suite, Test262~\cite{test262}.  After
    manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), which is the \textit{first IR-based formal
    semantics of modern JavaScript}, we found \inred{X}
    specification errors in ES10 and \inred{XX} wrong tests in Test262. They
    were all confirmed by TC39 and will be fixed in the next release.  After
    fixing them, the formal semantics passed all \inred{XX,XXX} applicable
    tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}

>>>>

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between the specification written in a
    natural language and tests.}
    To evaluate the correctness of \( \tool \), we checked the extracted
    semantics with the official test conformance suite, Test262~\cite{test262}.
    By manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), we define the \textit{first IR-based formal
    semantics of modern JavaScript}. It fails \inred{XXXX} tests because of the
    specification errors in ES10. We found eight specification errors and
    three of them are even not yet reported errors. They were all confirmed by
    TC39 and will be fixed in the next release.  After fixing them, the formal
    semantics passed all \inred{XX,XXX} applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}
